---
title: "Missing Data Analysis and Multiple Imputation Process"
author: "William Murrah"
format: html
editor: visual
bibliography: references-imputation.bib
---

```{r, message=FALSE, comment=NULL}
library(VIM)
library(mice)
load("~/qmer/Data/ECLS_K/2011/eclskimp.Rdata")
load("../../data/eclskmi5_removeSEScomp.Rdata")
```

The `eclsk_clean.Rdata` data file was used as the basis for generating the following subset of data for the missing data analysis and multiple imputation (see the R script `code/imputeECLSKclean.R`)."a

The following variables were used:

```{r}
names(eclskimp)
```

The procedures used to develop the multiple imputation process were based on @van2018flexible. First, we decided that the missing at random assumption was plausible, due to the extensive variables available in the ECLSK2011. To support this assumption the following missing data analysis was conducted.


```{r, out.width='200%'}
aggr(eclskimp, combined = TRUE, bars=FALSE)
```

```{r}
plot(eclskmi5)
```


```{r}
bwplot(eclskmi5)
```


```{r}
densityplot(eclskmi5)
```

